---
title: "Individual Assignment 7"
author: "Charlie Ling"
date: "10/29/2021"
output:
  word_document: default
  pdf_document: default
---

Problem #8: In the lab, a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable.

(a) Split the data set into a training set and a test set.
```{r}
library(ISLR)
Carseats=na.omit(Carseats)
fix(Carseats)
set.seed(3)
train=sample(nrow(Carseats),nrow(Carseats)/2)
test=-train
```


(b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?
```{r}
library(tree)
tree.Carseats = tree(Sales~.,Carseats,subset=train)
plot(tree.Carseats)
text(tree.Carseats,pretty=0)
summary(tree.Carseats)
tree.Carseats
```
```{r}
tree.pred=predict(tree.Carseats,Carseats[test,])
mean((tree.pred-Carseats$Sales[test])^2)
#test MSE is 4.784151
```



(c) Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?
```{r}
set.seed(3)
cv.Carseats=cv.tree(tree.Carseats)
names(cv.Carseats)
cv.Carseats
plot(cv.Carseats$size,cv.Carseats$dev,type="b")
# optimal tree size is 10
```
```{r}
prune.Carseats=prune.tree(tree.Carseats,best=10)
plot(prune.Carseats)
text(prune.Carseats,pretty=0)
tree.pred=predict(tree.Carseats,Carseats[test,])
mean((tree.pred-Carseats$Sales[test])^2)
#test MSE is 4.784151, which is the same as unpruned trees, so this pruning the tree does not improve the test MSE
```


