---
title: "Individual Assignment 1"
author: "Charlie Ling"
date: "9/1/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(MASS)
View(Boston)
?Boston
```


(a) How many rows are in this data set? How many columns? What
do the rows and columns represent?
```{r}
dim(Boston)
#506 rows and 14 columns, rows represent observations, columns present features
```


(b) Make some pairwise scatterplots of the predictors (columns) in
this data set. Describe your findings.
```{r}
pairs(Boston)
```
```{r}
m1=lm(nox~dis,data=Boston)
summary(m1)
#Buildings closer to  Boston employment centres have higher nitrogen oxides concentration.
```


```{r}
m2=lm(nox~age,data=Boston)
summary(m2)
#Older buildings have higher nitrogen oxides concentration.
```


(c) Are any of the predictors associated with per capita crime rate?
If so, explain the relationship.
```{r}
summary(lm(crim~tax,data=Boston))
#Tax. High tax makes people's life harder, maybe pushes them commit crimes.
```



(d) Do any of the suburbs of Boston appear to have particularly
high crime rates? Tax rates? Pupil-teacher ratios? Comment on
the range of each predictor.
```{r}
sapply(Boston,range)
```

```{r}
boxplot(Boston$crim)
#Some suburbs have particularly high crime rates because there are outliers in the crime boxplot.
```

```{r}
boxplot(Boston$tax)
```

```{r}
boxplot(Boston$ptratio)
```



(e) How many of the suburbs in this data set bound the Charles
river?
```{r}
sum(Boston$chas==1)
```

(f) What is the median pupil-teacher ratio among the towns in this
data set?
```{r}
median(Boston$ptratio)
```

(g) Which suburb of Boston has the lowest median value of owner-occupied
homes? What are the values of the other predictors
for that suburb, and how do those values compare to the overall
ranges for those predictors? Comment on your findings.
```{r}
n=which.min(Boston$medv)
n
Boston[n,1:13]
summary(Boston)
# Most of those values(such as crim, indus, nox, age, rad, tax, ptratio, black, 
# lstat)are above the 3rd quantile of overall ranges for those predictors, while rm,
# dis are reletively lower.
```


(h) In this data set, how many of the suburbs average more than
seven rooms per dwelling? More than eight rooms per dwelling?
Comment on the suburbs that average more than eight rooms
per dwelling.
```{r}
sum(Boston$rm>7)
sum(Boston$rm>8)
nums=which(Boston$rm>8)
Boston[nums,1:14]
# Those suburbs that average more than eight rooms per dwelling have low crime 
# rate, low lstat and high median value of owner-occupied homes.
```


