---
title: "Individual Assignment 11"
author: "Charlie Ling"
date: "2021/12/2"
output:
  word_document: default
  html_document: default
---

Exercise 10.7: Problem 9
ISLR p.417

9. Consider the USArrests data. We will now perform hierarchical clustering on the states.

(a) Using hierarchical clustering with complete linkage and Euclidean distance, cluster the states.
```{r}
library(ISLR)
df=na.omit(USArrests)
hc.complete = hclust(dist(df), method = "complete")
plot(hc.complete)
```

(b) Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?
```{r}
cutree(hc.complete,3)
```

(c) Hierarchically cluster the states using complete linkage and Euclidean distance, after scaling the variables to have standard deviation one.
```{r}
library(caret)
norm.values =preProcess(df,method = c("center", "scale"))
df.norm= predict(norm.values, df)
hc.complete = hclust(dist(df.norm), method = "complete")
plot(hc.complete)
cutree(hc.complete,3)
```

(d) What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer.
```{r}
#Scaling makes the cluster more evenly distributed and into more groups. As for this case, I do not think the variables should be scaled, because the scaled data are clustered into more than 3 groups. And the absolute value of crimes instead of scaled value is more useful to define the crime situation of a state.
```

