---
title: "Individual Assignment 2"
author: "Charlie Ling"
date: "9/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

10. This question should be answered using the Carseats data set.
```{r}
library(ISLR)
attach(Carseats)
View(Carseats)
```
(a) Fit a multiple regression model to predict Sales using Price, Urban, and US.
```{r}
lm.fit=lm(Sales~Price+Urban+US)
summary(lm.fit)
```


(b) Provide an interpretation of each coefficient in the model. Be careful—some of the variables in the model are qualitative!
```{r}
# Sales is negetively related to price.
# Us stores have higher sales
```

(c) Write out the model in equation form, being careful to handle the qualitative variables properly.
```{r}
# Sales=a+b1*Price+b2*Urban+b3*US
```


(d) For which of the predictors can you reject the null hypothesis H0:Bj=0?
```{r}
# For Price and US I can reject the null hypothesis H0:Bj=0
```


(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome.
```{r}
lm.fit1=lm(Sales~Price+US)
summary(lm.fit1)
```



(f) How well do the models in (a) and (e) fit the data?
```{r}
# The models in (a) and (e) have similar Adjusted R-squared: about 23%, which 
# means these two model fit the data not well.
```

(g) Using the model from (e), obtain 95% confidence intervals for the coefficient(s).
```{r}
confint(lm.fit1)
```


(h) Is there evidence of outliers or high leverage observations in the model from (e)?
```{r}
par(mfrow=c(2,2)) ##divide plotting region into 2*2

plot(lm.fit1)

par(mfrow=c(1,1)) ##reset plotting region
plot(predict(lm.fit1),rstudent(lm.fit1))

plot(hatvalues(lm.fit1)) ##Leverage
```
```{r}
# There are dots are on the far right side of the Residuals vs Leverage
# plot, which means potential high-leverage points
```

